---
title: "homework02"
author: "Brendan Zimmer"
date: "9/28/2021"
output: github_document
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(fig.path='Figs/')
```

#library
```{r}
library(nycflights13)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

#Looking at the different columns for flights
```{r}
glimpse(flights)
```
#1
```{r}
flights %>% 
  filter(is.na(dep_time))
```
#for dep_time there are 8,255 rows missing that have NA values.  This most likely means the plane never took off.  I believe this becasue the dep_delay, arr_time, arr_delay, air_time, and some tailnum also have NA values.  Some tailnum are recoreded when other columns have a NA, but I think this could be due to the plane arriving at the airport, probably getting checked in and then never leaving.  Also, I noticed that many of these flights are grouped up around the same day and sometimes time, I am not sure if that is significant or not though.

#2
```{r}
flights %>% 
  select(dep_time, sched_dep_time) %>% 
  mutate(dep_minutes_since_midnight = ((dep_time %/% 100)*60 + dep_time %% 100),
         sched_dep_minutes_since_midnight = ((sched_dep_time %/% 100)*60 + sched_dep_time %% 100))
```
#3
```{r}
cancelled_flights <- flights %>% 
  mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>% 
  group_by(year, month, day) %>% 
  summarise(
    cancelled_num = sum(cancelled),
    avg_cancelled = mean(cancelled),
    flights_num = n()
  )

cancelled_flights
```
```{r}
cancelled_delay_flights <- flights %>% 
  mutate(cancelled = is.na(dep_delay)) %>% 
  group_by(year, month, day) %>% 
  summarise(
    cancelled_prop = mean(cancelled),
    avg_dep_delay = mean(dep_delay, na.rm = TRUE)
  ) 

ggplot(cancelled_delay_flights) +
  geom_point(aes(x = avg_dep_delay, y = cancelled_prop))
```


#There is a definite decrease in flights every day execept in the first 3, while there is also an incrase of the number of flights.  There is also a strong positive relationship between avg_dep_delay and cancelled flights.  So yes they are related meaning most liekly as the average_dep_delay increase the average number of flights canceled also increases.

